On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-03 main.tex
Updated Section 6

We will let $\Phi$ be the mapping 

@@

defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Psi$ be the mapping

@@

    \Psi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

For all $(\xb,A) \in \Psi^{-1}(0),$ the Jacobian matrix of $\Psi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

The Jacobian of the system of polynomials $f,F_{1},\hdots,F_{n-i}$ is

@@

Since $\deg \Psi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Psi_{A}$, which means that 

@@

\jac_\textit{\textbf{x}} \Psi_A 
= \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)

@@

has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%

>>>>

We will let $\Phi$ be a mapping essentiall equal to 

@@

defines a radical ideal of dimension ? whose variety is smooth. Now, let $\Phi$ be the mapping

@@

    \Phi: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\

@@

For all $(\xb,A) \in \Phi^{-1}(0),$ the Jacobian matrix of $\Phi$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 

@@

so that the Jacobian is equal to

@@

Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $\td$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that 
\jac_\textit{\textbf{x}} \Phi_A &=\left(f(\xb),\grad(f(\xb))\cdot A_{i+1},\hdots. \grad(f(\xb))\cdot A_{n} \right) 
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). It follows that 

@@

 \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)

@@

also has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?). Therefore, for each $i \in \{1,\hdots,n\},$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.%
